Basic Bibliography and Reference Testing

### 2021-01-02 _support/reference/biblatex_basic/biblatex_test.tex
parencite date only, possessive citation

\usepackage{filecontents}
% This creates a bib file called ref.bib in the same folder as the current tex file
\begin{filecontents}{ref.bib}
@article{becker_human_1986,
	title = {Human Capital and the Rise and Fall of Families},
	volume = {4},
	url = {http://ideas.repec.org/a/ucp/jlabec/v4y1986i3ps1-39.html},
	pages = {S1--39},
	number = {3},
	journaltitle = {Journal of Labor Economics},
	author = {Becker, Gary S and Tomes, Nigel},
	urldate = {2012-02-15},
	date = {1986}
}
@article{case_lasting_2005,
	title = {The lasting impact of childhood health and circumstance},
	volume = {24},
	issn = {0167-6296},
	url = {http://www.ncbi.nlm.nih.gov/pubmed/15721050},
	doi = {10.1016/j.jhealeco.2004.09.008},
	pages = {365--389},
	number = {2},
	journaltitle = {Journal of health economics},
	shortjournal = {J Health Econ},
	author = {Case, Anne and Fertig, Angela and Paxson, Christina},
	urldate = {2012-06-13},
	date = {2005-03},
	pmid = {15721050},
	keywords = {Adult, child, Child Welfare, Cohort Studies, Great Britain, Health Status Indicators, Humans, Social Class}
}
@article{conti_understanding_2010,
	title = {Understanding the Early Origins of the Education–Health Gradient},
	volume = {5},
	issn = {1745-6916, 1745-6924},
	url = {http://pps.sagepub.com/content/5/5/585.abstract},
	doi = {10.1177/1745691610383502},
	pages = {585--605},
	number = {5},
	journaltitle = {Perspectives on Psychological Science},
	author = {Conti, Gabriella and Heckman, James J},
	urldate = {2012-02-16},
	date = {2010-09-01},
	keywords = {health, education, genetics, treatment effects}
}
\end{filecontents}

@@

\paragraph{\href{https://papers.ssrn.com/sol3/papers.cfm?abstract_id=3140132}{Data}}

>>>>

\usepackage{filecontents}
% This creates a bib file called ref.bib in the same folder as the current tex file
\begin{filecontents}{ref.bib}
@article{becker_human_1986,
	title = {Human Capital and the Rise and Fall of Families},
	volume = {4},
	url = {http://ideas.repec.org/a/ucp/jlabec/v4y1986i3ps1-39.html},
	pages = {S1--39},
	number = {3},
	journaltitle = {Journal of Labor Economics},
	author = {Becker, Gary S and Tomes, Nigel},
	urldate = {2012-02-15},
	date = {1986}
}
@article{case_lasting_2005,
	title = {The lasting impact of childhood health and circumstance},
	volume = {24},
	issn = {0167-6296},
	url = {http://www.ncbi.nlm.nih.gov/pubmed/15721050},
	doi = {10.1016/j.jhealeco.2004.09.008},
	pages = {365--389},
	number = {2},
	journaltitle = {Journal of health economics},
	shortjournal = {J Health Econ},
	author = {Case, Anne and Fertig, Angela and Paxson, Christina},
	urldate = {2012-06-13},
	date = {2005-03},
	pmid = {15721050},
	keywords = {Adult, child, Child Welfare, Cohort Studies, Great Britain, Health Status Indicators, Humans, Social Class}
}
@article{conti_understanding_2010,
	title = {Understanding the Early Origins of the Education–Health Gradient},
	volume = {5},
	issn = {1745-6916, 1745-6924},
	url = {http://pps.sagepub.com/content/5/5/585.abstract},
	doi = {10.1177/1745691610383502},
	pages = {585--605},
	number = {5},
	journaltitle = {Perspectives on Psychological Science},
	author = {Conti, Gabriella and Heckman, James J},
	urldate = {2012-02-16},
	date = {2010-09-01},
	keywords = {health, education, genetics, treatment effects}
}
@article{hao_air_2016,
	title = {Air {Pollution} and {Preterm} {Birth} in the {U}.{S}. {State} of {Georgia} (2002–2006): {Associations} with {Concentrations} of 11 {Ambient} {Air} {Pollutants} {Estimated} by {Combining} {Community} {Multiscale} {Air} {Quality} {Model} ({CMAQ}) {Simulations} with {Stationary} {Monitor} {Measurements}},
	volume = {124},
	issn = {0091-6765, 1552-9924},
	shorttitle = {Air {Pollution} and {Preterm} {Birth} in the {U}.{S}. {State} of {Georgia} (2002–2006)},
	url = {https://ehp.niehs.nih.gov/doi/10.1289/ehp.1409651},
	doi = {10.1289/ehp.1409651},
	language = {en},
	number = {6},
	urldate = {2020-07-18},
	journal = {Environmental Health Perspectives},
	author = {Hao, Hua and Chang, Howard H. and Holmes, Heather A. and Mulholland, James A. and Klein, Mitch and Darrow, Lyndsey A. and Strickland, Matthew J.},
	month = jun,
	year = {2016},
	pages = {875--880}
}
@article{westergaard_ambient_2017,
	title = {Ambient air pollution and low birth weight - are some women more vulnerable than others?},
	volume = {104},
	issn = {01604120},
	url = {https://linkinghub.elsevier.com/retrieve/pii/S0160412017301976},
	doi = {10.1016/j.envint.2017.03.026},
	language = {en},
	urldate = {2020-07-19},
	journal = {Environment International},
	author = {Westergaard, Nadja and Gehring, Ulrike and Slama, Rémy and Pedersen, Marie},
	month = jul,
	year = {2017},
	pages = {146--154},
}

\end{filecontents}

@@

\section{Possessive Citations}

In this example, using possessive to put apostrophe after author names and before date. Accomplished by using \emph{citeauthor} first then \emph{parentcite}.

\citeauthor{hao_air_2016}'s \parencite*{hao_air_2016} Georgia study
found that associations of traffic-related pollutants, including NO\textsubscript{2} and
PM\textsubscript{2.5}, with preterm birth tended to be stronger for mothers with low
educational attainment.

\section{Cite Only Date}

To write more flexibly, can mention author names explicitly in text and then cite the article with \emph{parentcite} for the date only: Westergaard and her colleagues \parencite*{westergaard_ambient_2017} identified only a small handful of studies that addressed effect modification by dimensions of socioeconomic status.

\section{\href{https://papers.ssrn.com/sol3/papers.cfm?abstract_id=3140132}{Data}}
